My First R Markdown File
========================

This is the course project 1 for Reproducible Research course.

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, results = "asis")
```

####1. reading in the dataset and processing the data
```{r loaddata}
data <- read.csv("activity.csv", header = TRUE, sep = ",")
```

####2. histogram of the total number of steps taken each day
```{r histoftotalsteps, results='asis'}
totalsteps<- with(data,tapply(steps,date,sum,na.rm=T))
hist(totalsteps)
```

####3. Mean and median number of the total steps taken each day
```{r meanandmedianofsteps, results='asis'}
mean(totalsteps)
median(totalsteps)
```

####4. Time series plot of the average number of steps taken
```{r}
library(dplyr)
avesteps <- data %>% group_by(interval) %>% summarize(avesteps=mean(steps,na.rm=TRUE))
plot(avesteps,type="l",xlab="5 mins Per Interval", ylab="Average Steps", main ="Average Steps Per Interval")
```

####5. The 5-minute interval that, on average, contains the maximum number of steps
```{r}
avesteps$interval[which.max(avesteps$avesteps)]
```

####6. Code to describe and show a strategy for imputing missing data
```{r}
sum((rowSums(is.na(data)))>=1)
newdata<-merge(data,avesteps,by="interval",all=TRUE)
index<-is.na(newdata$steps)
newdata$steps[index]<-newdata$avesteps[index]
newdata<-newdata[order(newdata$date),1:3]
```

####7. Histogram of the total number of steps taken each day after missing values are imputed
```{r}
totalstepsnew<- with(newdata,tapply(steps,date,sum,na.rm=T))
hist(totalstepsnew)
mean(totalstepsnew)
median(totalstepsnew)
```

####8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
library(lattice)
Sys.setlocale("LC_TIME","C")
newdata$date<-as.Date(newdata$date)
weekend<-weekdays(newdata$date) %in% c("Saturday","Sunday")
newdata$weeks<-factor(weekend,labels=c("weekday","weekend"))
aveactivitydata<-aggregate(steps~interval+weeks,data=newdata,FUN="mean")
with(aveactivitydata,xyplot(steps~interval|weeks,layout=c(1,2),type="l",ylab="Number of steps",xlab="Interval"))
```

####9. All the R code needed to reproduce the results in the report
